---
title: "Stream_Segment_Upstream"
author: "Corey White"
date: "01/18/2020"
output:
  md_document:
    variant: gfm
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libs, include=FALSE}
library(tidyr)

library(ggplot2)
library(ggpubr) # 'ggplot2' Based Publication Ready Plots
# library(matrixStats) # Functions that Apply to Rows and Columns of Matrices (and to Vectors)
library(pacman) # Package Management Tool
library(cowplot) # add-on to ggplot. It provides various features that help with creating publication-quality 
library(RColorBrewer)
library(rgeos)
library(sf)
library(rgrass7)
library(rgdal)
require(gridExtra)

```


# Stream Segment Analysis

Investigate the differnce between contributing areas for stream segments with and without stream buffers.

## Data

* QL2 3M DEM
* Load Monitoring Sites
* Land-Use we can either use NWALT or NLCD

## Methods

Connect to GRASS
```{r}
# initialisation of GRASS in the North Carolina sample dataset
#6542
rgrass7::initGRASS(gisBase = "/usr/lib/grass76", 
          home = tempdir(), 
          gisDbase = "../../grassdata",
          location="wrri_nad83_6542",
          mapset="wrri10m",
          override = TRUE)
```


```{r}
rgrass7::execGRASS("g.region", parameters= list(vector = "subwatersheds", res="10"), flags =c("p"))
```

# MASK Already set
```{r}
#rgrass7::execGRASS("r.mask", parameters = list(raster = "MASK"))
```


# Import QLD 10m DEMs and create mosaic for the study area.


1. Calculate stream segments.

Use GRASS GIS r.watershed to get stream flow accumulation, streams,

[r.stream.segment](https://grass.osgeo.org/grass78/manuals/addons/r.stream.segment.html

Layer Names

```{r}
dem <- "dem_10m_mosaic" #Patched DEM
res < - 10 #meters

# r.watershed config
basin_threshold <- 10000

# r.watershed outputs
drainage <- "direction_10k"
streams <- "streams_10k" 
basins <- "basins_10k" 
accumulation <-"accumulation_10k"


```


```{r}
# Shell GRASS Example
#g.region -p -a raster=elevation
#r.watershed elevation=elevation threshold=10000 drainage=direction_10k stream=streams
#r.stream.order stream_vect=streams direction=direction_10k strahler=riverorder_strahler
#r.stream.segment stream_rast=riverorder_strahler direction=direction_10k \
#  elevation=elevation segments=river_segment sectors=river_sector
rgrass7::execGRASS("g.region", parameters = list(raster=dem, res=res))
rgrass7::execGRASS("r.watershed", 
                   parameters = list(
                     elevation=dem, 
                     threshold=basin_threshold,
                     drainage=drainage, 
                     stream=streams, 
                     basin=basins,
                     accumulation=accumulation,
                     memory=6500
                    ),
                   flags = c("m")
                   )
rgrass7::execGRASS("db.connect", flags = c("p"))
```

2. Calculate the contributing area.

[r.water.outlet](https://grass.osgeo.org/grass79/manuals/r.water.outlet.html)


```{r}
# the watershed outlet position should be placed on a stream (from
# accumulation map):
# r.water.outlet input=direction_10k output=basin coordinates=<east,north>
```

3. Calculate total area of defined land-use in contributing area.


```{r}
df_nwalt_subwatershed_1992 <- read.table(
  "nwalt_subwatershed_1992.csv",
  sep=",", 
  header=FALSE,
  col.names=c("site_num", "site_id","landclass","unk1", "area_sqm", "cell_count"))

df_nwalt_subwatershed_2012 <- read.table(
  "nwalt_subwatershed_2012.csv",
  sep=",", 
  header=FALSE,
  col.names=c("site_num", "site_id","landclass","unk1", "area_sqm", "cell_count"))


# Add year field to dataframes
df_nwalt_subwatershed_1992$year <- as.Date("01/01/1992", format="%m/%d/%Y")
df_nwalt_subwatershed_2012$year <- as.Date("01/01/2012", format="%m/%d/%Y")

# Merge each year into a signle dataframe
df_nwalt_subwatershed <- bind_rows(df_nwalt_subwatershed_1992,df_nwalt_subwatershed_2012)

# ref https://pubs.usgs.gov/ds/0948/ds948.pdf page 7
nwalt_class_map <- c(
    "Water"=11,
    "Wetlands"=12,
    "Major Transportation"=21,
    "Commercial/Services"=22,
    "Industrial/Military"=23,
    "Recreation"=24,
    "Residential, High Density"=25,
    "Residential, Low-Medium Density"=26,
    "Developed, Other"=27,
    "Urban Interface High"=31,
    "Urban Interface Low Medium"=32,
    "Anthropogenic Other"=33,
    "Mining/Extraction"=41,
    "Timber and Forest Cutting (1992-2012 only)"= 42,
    "Crops"=43,
    "Pasture/Hay"=44,
    "Grazing Potential"=45,
    "Low Use"=50,
    "Very Low Use, Conservation"=60
)

# Create factor for nwalt classes
df_nwalt_subwatershed$landclass_factor <- as.factor(haven::labelled(
  df_nwalt_subwatershed$landclass,
  labels = nwalt_class_map))


df_nwalt_subwatershed %>%
  filter(site_num == 1) %>%
  ggplot(aes(year,area_sqm, color=landclass_factor)) +
   geom_line() +
   geom_point()
```

4. Compare land-use in contributing areas from buffered and unbuffered stream segments.
```{r}
# Use calcuated data to analysize if a statistical difference exists between land-use distribution in the contributing 
# areas a buffered vs. unbuffered stream segments.
```

5. Create Variable Flood Plain Map

Generate the partial derivative dx and dy
```{r}
slope <- "slope"
aspect <- "aspect"
dx <- "dx"
dy <- "dy"
rgrass7::execGRASS("r.slope.aspect",
                   parameters=list(
                    elevation=dem,
                    slope=slope,
                    aspect=aspect,
                    dx=dx,
                    dy=dy
                  )
)

```


Set manning values form 

```{r}
rgrass7::execGRASS("r.recode",
                   parameters = list(
                     input=nwalt_data,
                     output=mancover,
                     rules="./nwalt_to_mannings.txt"
                   ))
```


r.recode input=NLCD_2016_Land_Cover_L48_20190424@wrri output=raincover rules=./nlcd_to_rain.txt

```{r}
rgrass7::execGRASS("r.recode",
                   parameters = list(
                     input=nwalt_data,
                     output=raincover,
                     rules="./nwalt_to_raincover.txt"
                   ))
```

r.sim.water -t -s --overwrite elevation=dem_mosaic@PERMANENT dx=dx@wrri dy=dy@wrri rain=raincover@wrri man=mancover@wrri depth=HR6_depth discharge=HR6_disch nwalkers=1000000 niterations=30 random_seed=5 nprocs=14

```{r}
rgrass7::execGRASS("r.sim.water",
                   parameters = list(
                     elevation=dem,
                     dx=dx,
                     dy=dy,
                     rain="raincover",
                     man="mancover",
                     depth="depth",
                     discharge="disch",
                     nwalkers=1000000,
                     niteraction=30,
                     random_seed=5,
                     nprocs=14
                     ),
                     flags=c("overwrite", "t", "s")
                   )
```


Create vartiable Floodplain
r.mapcalc --overwrite expression=HR6_depth_filtered = if(HR6_depth.29@wrri >= 0.05, 1, null())

```{r}

rgrass7::execGRASS("r.mapcalc", parameters = list(
  expression="depth_filtered = if(depth.29 >= 0.05,1, null())"
))
```


r.neighbors -c --overwrite input=HR6_depth_filtered@wrri output=moving_stream_buffer method=median size=9

```{r}


rgrass7::execGRASS("r.neighbors",
                   parameters = list(
                     input="depth_filtered",
                     output="moving_stream_buffer",
                     method="median",
                     size=9
                   ),
                   flags=c("overwrite", "c")
                   )
```

## Results


