---
title: "Stream_Segment_Upstream"
author: "Corey White"
date: "01/18/2020"
output:
  md_document:
    variant: gfm
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libs, include=FALSE}
library(tidyr)

library(ggplot2)
library(ggpubr) # 'ggplot2' Based Publication Ready Plots
# library(matrixStats) # Functions that Apply to Rows and Columns of Matrices (and to Vectors)
library(pacman) # Package Management Tool
library(cowplot) # add-on to ggplot. It provides various features that help with creating publication-quality 
library(RColorBrewer)
library(rgeos)
library(sf)
require(rgrass7)
library(rgdal)
require(gridExtra)

```


# Stream Segment Analysis

Investigate the differnce between contributing areas for stream segments with and without stream buffers.

## Data

* QL2 3M DEM
* Load Monitoring Sites
* Land-Use we can either use NWALT or NLCD

## Methods

Connect to GRASS
```{r initgrass, eval=FALSE}
# initialisation of GRASS in the North Carolina sample dataset
#6542
rgrass7::initGRASS(gisBase = "/usr/lib/grass76", 
          home = tempdir(), 
          gisDbase = "../../grassdata",
          location="wrri_nad83_6542",
          mapset="wrri10m",
          override = TRUE)
```
```{r listvectors, eval=FALSE}
rgrass7::execGRASS("g.list", parameters = list(type = "vector"))
```

```{r listRasters, eval=FALSE}
rgrass7::execGRASS("g.list", parameters = list(type = "raster"))
```


```{r}
rgrass7::execGRASS("g.region", parameters= list(vector = "subwatersheds", res="10"), flags =c("p"))
```



# MASK Already set
```{r, eval=FALSE}
rgrass7::execGRASS("r.mask", flags = c("r"))
rgrass7::execGRASS("r.mask", parameters = list(vector="subwatersheds"))
```


# Import QLD 10m DEMs and create mosaic for the study area.


1. Calculate stream segments.

Use GRASS GIS r.watershed to get stream flow accumulation, streams,

[r.stream.segment](https://grass.osgeo.org/grass78/manuals/addons/r.stream.segment.html

Layer Names

```{r parameters, eval = FALSE}

dem <- "dem_10m_mosaic" #Patched DEM
res <- 10 #meters

# r.watershed config
basin_threshold <- 10000

# r.watershed outputs
drainage <- "direction_10k"
streams <- "streams_10k" 
basins <- "basins_10k" 
accumulation <-"accumulation_10k"


```


```{r watershed, eval = FALSE}
# Shell GRASS Example
#g.region -p -a raster=elevation
#r.watershed elevation=elevation threshold=10000 drainage=direction_10k stream=streams
#r.stream.order stream_vect=streams direction=direction_10k strahler=riverorder_strahler
#r.stream.segment stream_rast=riverorder_strahler direction=direction_10k \
#  elevation=elevation segments=river_segment sectors=river_sector
rgrass7::execGRASS("g.region", parameters = list(raster=dem, res=res))
rgrass7::execGRASS("r.watershed", 
                   parameters = list(
                     elevation=dem, 
                     threshold=basin_threshold,
                     drainage=drainage, 
                     stream=streams, 
                     basin=basins,
                     accumulation=accumulation,
                     memory=6500
                    ),
                   flags = c("m")
                   )
```

Calculate Stream Buffer

```{r create5kstreamBuffer30m, eval=FALSE}
stream_buffer <- paste0(streams,"_", buffer_dist,"m")
buffer_dist <- 15 # radius in meters
rgrass7::execGRASS("r.buffer",
                   parameters = list(
                     input=paste(streams,"thin", sep="_"),
                     output=paste0(streams,"_", buffer_dist * 2,"m"),
                     distances= buffer_dist,
                     units="meters"
                   ),
                   flags=c("overwrite"))
  
```


2. Calculate the contributing area.

[r.water.outlet](https://grass.osgeo.org/grass79/manuals/r.water.outlet.html)


```{r}
# the watershed outlet position should be placed on a stream (from
# accumulation map):
# r.water.outlet input=direction_10k output=basin coordinates=<east,north>
```

3. Calculate total area of defined land-use in contributing area.

```{r calculateLanduse, eval=TRUE}

calucuteLandUsePerSubwatershed <- function(date_range, landuse_file_prefix, subwatershed_csv_prefix, landuse_class_map) {
  df_landuse_subwatershed <- NULL
  #Loop through each year of landuse data and calculate the total landuse area of each class per subwatershed per year. Return a single dataframe containing values for each year.
  for(year in date_range) {
    input <- paste0("subwatersheds,",landuse_file_prefix, year, "@wrri10m")
    output <- paste0(subwatershed_csv_prefix, year, ".csv")
    nwalt_date <- paste0("01/01/", year)
    
    # Create csv with total landuse area by subwatershed
    rgrass7::execGRASS("r.stats", parameters = list(input=input, separator=",", output=output), flags = c("a","c","l", "n", "overwrite"))
    
    # Load the cvs that was just made into an r dataframe
    tmp_df_subwatershed <- read.table(
    output,
    sep=",", 
    header=FALSE,
    col.names=c("site_num", "site_id","landclass","unk1", "area_sqm", "cell_count"))
    
    # Add a year field with the landuse data year
    tmp_df_subwatershed$year <- as.Date(nwalt_date, format="%m/%d/%Y")
    
    # If it's the first time through the loop set the varibale to the new dataframe otherwise bind the rows of the dataframes together
    if (is.null(df_landuse_subwatershed)) {
      df_landuse_subwatershed <- tmp_df_subwatershed
    } else {
      df_landuse_subwatershed <- bind_rows(df_landuse_subwatershed,tmp_df_subwatershed)
    }
  }
  
  
  
  # Create factor for nwalt classes
  df_landuse_subwatershed$landclass_factor <- as.factor(haven::labelled(
    df_landuse_subwatershed$landclass,
    labels = landuse_class_map))
    
  return(df_landuse_subwatershed)
}



```

```{r nwalt_subwatershed}
# ref https://pubs.usgs.gov/ds/0948/ds948.pdf page 7
nwalt_class_map <- c(
    "Water"=11,
    "Wetlands"=12,
    "Major Transportation"=21,
    "Commercial/Services"=22,
    "Industrial/Military"=23,
    "Recreation"=24,
    "Residential, High Density"=25,
    "Residential, Low-Medium Density"=26,
    "Developed, Other"=27,
    "Urban Interface High"=31,
    "Urban Interface Low Medium"=32,
    "Anthropogenic Other"=33,
    "Mining/Extraction"=41,
    "Timber and Forest Cutting (1992-2012 only)"= 42,
    "Crops"=43,
    "Pasture/Hay"=44,
    "Grazing Potential"=45,
    "Low Use"=50,
    "Very Low Use, Conservation"=60
)


nwalt_years <- c("1974", "1982", "1992", "2002", "2012")
nwalt_prefix <- "nwalt_landuse_"
nwalt_subwatershed_csv_prefix <-"nwalt_subwatershed_"

df_nwalt_subwatershed <- calucuteLandUsePerSubwatershed(nwalt_years,nwalt_prefix,nwalt_subwatershed_csv_prefix, nwalt_class_map)

```

```{r}

df_nwalt_subwatershed <- mutate(df_nwalt_subwatershed,nwalt_class_label=recode(landclass, 
                         `11`=  "Water",
                         `12`=  "Wetlands",
                         `21` = "Developed, Major Transportation",
                         `22` = "Developed, Commercial/Services",
                         `23` = "Developed, Industrial/Military",
                         `24` = "Developed, Recreation",
                         `25` = "Developed, Residential, High",
                         `26` = "Developed, Residential, Low-Medium",
                         `27` = "Developed, Other",
                         `31` = "Semi-developed, urb interface high",
                         `32` = "Semi-developed, urb interface low-med",
                         `33` = "Semi-developed, anthropogenic other",
                         `41` = "Production, mining",
                         `42` = "Prodution, timber and forest cutting",
                         `43` = "Production, crops",
                         `44` = "Production, pasture/hay",
                         `45` = "Production, grazing potential",
                         `50` = "Low usage",
                         `60` = "Very low usage, conservation"
                         ))

nwalt_class_colors <- c(
  "Water" = "#526fa3",
  "Wetlands" = "#b8d9ec",
  "Developed, Major Transportation" = "#010101",
  "Developed, Commercial/Services" = "#00c7f9",
  "Developed, Industrial/Military" = "#002579",
  "Developed, Recreation" = "#d2ffb8",
  "Developed, Residential, High" = "#aa0000",
  "Developed, Residential, Low-Medium" = "#f87a7b",
  
  "Developed, Other" = "#fbbfbe",
  "Semi-developed, urb interface high" = "#ffa607",
  "Semi-developed, urb interface low-med" = "#ffebc0",
  "Semi-developed, anthropogenic other" = "#b2b2b2",
  "Production, mining" = "#4e4e4e",
  "Prodution, timber and forest cutting" = "#b8e62f",
  "Production, crops" = "#b26c30",
  "Production, pasture/hay" = "#dcd443",
  "Production, grazing potential" = "#faff01",
  "Low usage" = "#4de600",
  "Very low usage, conservation" = "#39a600"
  )

df_nwalt_subwatershed %>%
  filter(site_num == 23) %>%
  group_by(year, nwalt_class_label) %>%
  summarize(sum = sum(area_sqm)) %>%
  mutate(km=sum / 1e6) %>%
  ggplot(aes(year,km, color=nwalt_class_label)) +
  geom_line() +
  geom_point() +
  #stat_smooth() +
  labs(color="NWALT Classification",
       title = "NWALT Land Use",
       subtitle = "Subwatershed A23 from 1974 to 2012",
       x = "Year",
       y = "Area (km2)") +
  scale_color_manual(values = nwalt_class_colors)
```


```{r landuseA1}

df_nwalt_subwatershed <- mutate(df_nwalt_subwatershed,wrriclass=recode(landclass, 
                         `11`= "Undeveloped",
                         `12`= "Undeveloped",
                         `21` = "Urban",
                         `22` = "Urban",
                         `23` = "Urban",
                         `24` = "Urban",
                         `25` = "Urban",
                         `26` = "Urban",
                         `27` = "Urban",
                         `31` = "Undeveloped",
                         `32` = "Undeveloped",
                         `33` = "Undeveloped",
                         `41` = "Undeveloped",
                         `42` = "Undeveloped",
                         `43` = "Agriculture",
                         `44` = "Agriculture",
                         `45` = "Undeveloped",
                         `50` = "Undeveloped",
                         `60` = "Undeveloped"
                         ))

nwalt_reclass_colors <- c(
  "Agriculture" = "#e1da43",
  "Undeveloped" = "#36a508",
  "Urban" = "#ff7c7c"
  )

df_nwalt_subwatershed %>%
  filter(site_num == 23) %>%
  group_by(year, wrriclass) %>%
  summarize(sum = sum(area_sqm)) %>%
  mutate(km=sum / 1e6) %>%
  ggplot(aes(year,km, color=wrriclass)) +
  geom_line() +
  geom_point() +
  #stat_smooth() +
  labs(color="NWALT Classification",
       title = "NWALT Land Use",
       subtitle = "Subwatershed A23 from 1974 to 2012",
       x = "Year",
       y = "Area (km2)") +
  scale_color_manual(values = nwalt_reclass_colors)


df_nwalt_subwatershed %>%
  filter(site_num == 22) %>%
  group_by(year, wrriclass) %>%
  summarize(sum = sum(area_sqm)) %>%
  mutate(km=sum / 1e6) %>%
  ggplot(aes(year,km, color=wrriclass)) +
  geom_line() +
  geom_point() +
  #stat_smooth() +
  labs(color="NWALT Classification",
       title = "NWALT Land Use",
       subtitle = "Subwatershed A23 from 1974 to 2012",
       x = "Year",
       y = "Area (km2)") +
  scale_color_manual(values = nwalt_reclass_colors)
```



```{r}
df_nwalt_subwatershed %>%
  filter(site_num == 1) %>%
  ggplot(aes(year,area_sqm, color=landclass_factor)) +
   geom_line() +
   geom_point() +
  labs(color="NWALT Classification",
       title = "NWALT Land Use for Subwatershed A1",
       subtitle = "from 1974 to 2012",
       x = "Year",
       y = "Area (m2)")
```

```{r, fig.width=15, fig.height= 25, fig.align='center'}
df_nwalt_subwatershed %>%
  group_by(year,site_id, wrriclass) %>%
  summarize(sum = sum(area_sqm)) %>%
  mutate(km=sum / 1e6) %>%
  ggplot(aes(year,km, color=wrriclass)) +
  facet_wrap(site_id~., ncol = 6) +
   geom_line() +
   geom_point() +
  #scale_y_continuous(trans='log10') +
  labs(color="NWALT Classification",
       title = "NWALT Land Use for Subwatersheds",
       subtitle = "from 1974 to 2012",
       x = "Year",
       y = "Area (km2)") +
  scale_color_manual(values = nwalt_reclass_colors)
```

4. Compare land-use in subwatershed areas from buffered and unbuffered stream segments.
```{r}
# Use calcuated data to analysize if a statistical difference exists between land-use distribution in the contributing 
# areas a buffered vs. unbuffered stream segments.

rgrass7::execGRASS("r.mask", flags = c("r"))
rgrass7::execGRASS("r.mask", parameters = list(raster = stream_buffer))
```

```{r}
nwalt_years <- c("1974", "1982", "1992", "2002", "2012")
nwalt_prefix <- "nwalt_landuse_"
nwalt_subwatershed_csv_prefix <-"nwalt_subwatershed_30m_rip_buffer_"
df_nwalt_subwatershed_30m_rip_buffer <- calucuteLandUsePerSubwatershed(nwalt_years,nwalt_prefix,nwalt_subwatershed_csv_prefix, nwalt_class_map)
```

Examine with A1 subwatershed

```{r}

df_nwalt_subwatershed_30m_rip_buffer <- mutate(df_nwalt_subwatershed_30m_rip_buffer,wrriclass=recode(landclass, 
                         `11`= "Undeveloped",
                         `12`= "Undeveloped",
                         `21` = "Urban",
                         `22` = "Urban",
                         `23` = "Urban",
                         `24` = "Urban",
                         `25` = "Urban",
                         `26` = "Urban",
                         `27` = "Urban",
                         `31` = "Undeveloped",
                         `32` = "Undeveloped",
                         `33` = "Undeveloped",
                         `41` = "Undeveloped",
                         `42` = "Undeveloped",
                         `43` = "Agriculture",
                         `44` = "Agriculture",
                         `45` = "Undeveloped",
                         `50` = "Undeveloped",
                         `60` = "Undeveloped"
                         ))

nwalt_reclass_colors <- c(
  "Agriculture" = "#e1da43",
  "Undeveloped" = "#36a508",
  "Urban" = "#ff7c7c"
  )

df_nwalt_subwatershed_30m_rip_buffer %>%
  filter(site_num == 23) %>%
  group_by(year, wrriclass) %>%
  summarize(sum = sum(area_sqm)) %>%
  mutate(km=sum / 1e6) %>%
  ggplot(aes(year,km, color=wrriclass)) +
  geom_line() +
  geom_point() +
  labs(color="NWALT Classification",
       title = "NWALT Land Use within 10m DEM Derived (10k) 30m Stream Buffer",
       subtitle = "Subwatershed A23 from 1974 to 2012",
       x = "Year",
       y = "Area (km2)") +
  scale_color_manual(values = nwalt_reclass_colors)

df_nwalt_subwatershed_30m_rip_buffer %>%
  filter(site_num == 22) %>%
  group_by(year, wrriclass) %>%
  summarize(sum = sum(area_sqm)) %>%
  mutate(km=sum / 1e6) %>%
  ggplot(aes(year,km, color=wrriclass)) +
  geom_line() +
  geom_point() +
  labs(color="NWALT Classification",
       title = "NWALT Land Use within 10m DEM Derived (10k) 30m Stream Buffer",
       subtitle = "Subwatershed A22 from 1974 to 2012",
       x = "Year",
       y = "Area (km2)") +
  scale_color_manual(values = nwalt_reclass_colors)

```

Show all subwatersheds

```{r, fig.width=15, fig.height= 25, fig.align='center'}

df_nwalt_subwatershed_30m_rip_buffer %>%
  group_by(year,site_id, wrriclass) %>%
  summarize(sum = sum(area_sqm)) %>%
  mutate(km=sum / 1e6) %>%
  ggplot(aes(year,km, color=wrriclass)) +
  facet_wrap(site_id~., ncol = 6) +
   geom_line() +
   geom_point() +
  #scale_y_continuous(trans='log10') +
  labs(color="NWALT Classification",
       title = "NWALT Land Use within 30m Stream Buffer for Subwatersheds",
       subtitle = "from 1974 to 2012",
       x = "Year",
       y = "Area (km2)") +
  scale_color_manual(values = nwalt_reclass_colors)
```

### nhd_plus_flowlines_piedmont_cliped

```{r, eval=FALSE}
rgrass7::execGRASS("r.mask", flags = c("r"))
rgrass7::execGRASS("r.mask", parameters = list(vector="subwatersheds"))
```

```{r}
rgrass7::execGRASS('v.to.rast', 
                   parameters = list(
                     input="nhd_plus_flowlines_piedmont_cliped",
                     output="nhd_plus_flowlines",
                     use="val"
                     ), 
                   flags = c("overwrite")
                )

nhd_plus_stream_buffer <- "nhd_plus_flowlines_stream_buffer_30m"
buffer_dist <- 15 # radius in meters
rgrass7::execGRASS("r.buffer",
                   parameters = list(
                     input="nhd_plus_flowlines",
                     output=nhd_plus_stream_buffer,
                     distances= buffer_dist,
                     units="meters"
                   ),
                   flags=c("overwrite"))

```

```{r, eval=FALSE}
rgrass7::execGRASS("r.mask", flags = c("r"))
rgrass7::execGRASS("r.mask", parameters = list(raster="nhd_plus_flowlines_stream_buffer_30m"))
```



```{r, eval=FALSE}


nwalt_subwatershed_nhd_plus_csv_prefix <-"nwalt_subwatershed_nhd_plus_30m_rip_buffer_"
df_nwalt_subwatershed_nhd_plus_30m_rip_buffer <- calucuteLandUsePerSubwatershed(nwalt_years,nwalt_prefix,nwalt_subwatershed_nhd_plus_csv_prefix, nwalt_class_map)
```

Examine with A1

```{r}

df_nwalt_subwatershed_nhd_plus_30m_rip_buffer <- mutate(df_nwalt_subwatershed_nhd_plus_30m_rip_buffer,wrriclass=recode(landclass, 
                         `11`= "Undeveloped",
                         `12`= "Undeveloped",
                         `21` = "Urban",
                         `22` = "Urban",
                         `23` = "Urban",
                         `24` = "Urban",
                         `25` = "Urban",
                         `26` = "Urban",
                         `27` = "Urban",
                         `31` = "Undeveloped",
                         `32` = "Undeveloped",
                         `33` = "Undeveloped",
                         `41` = "Undeveloped",
                         `42` = "Undeveloped",
                         `43` = "Agriculture",
                         `44` = "Agriculture",
                         `45` = "Undeveloped",
                         `50` = "Undeveloped",
                         `60` = "Undeveloped"
                         ))

nwalt_reclass_colors <- c(
  "Agriculture" = "#e1da43",
  "Undeveloped" = "#36a508",
  "Urban" = "#ff7c7c"
  )

df_nwalt_subwatershed_nhd_plus_30m_rip_buffer %>%
  filter(site_num == 23) %>%
  group_by(year, wrriclass) %>%
  summarize(sum = sum(area_sqm)) %>%
  mutate(km=sum / 1e6) %>%
  ggplot(aes(year,km, color=wrriclass)) +
  geom_line() +
  geom_point() +
  labs(color="NWALT Classification",
       title = "NWALT Land Use within NHDPlus 30m Stream Buffer",
       subtitle = " Subwatershed A23 from 1974 to 2012",
       x = "Year",
       y = "Area (km2)") +
  scale_color_manual(values = nwalt_reclass_colors)

df_nwalt_subwatershed_nhd_plus_30m_rip_buffer %>%
  filter(site_num == 22) %>%
  group_by(year, wrriclass) %>%
  summarize(sum = sum(area_sqm)) %>%
  mutate(km=sum / 1e6) %>%
  ggplot(aes(year,km, color=wrriclass)) +
  geom_line() +
  geom_point() +
  labs(color="NWALT Classification",
       title = "NWALT Land Use within NHDPlus 30m Stream Buffer",
       subtitle = " Subwatershed A22 from 1974 to 2012",
       x = "Year",
       y = "Area (km2)") +
  scale_color_manual(values = nwalt_reclass_colors)

```

view stream data

```{r}
```


## Predicit Missing Values 

```{r}
ggplot(df_nwalt_subwatershed_30m_rip_buffer, aes(x=area_sqm)) + geom_histogram()
ggplot(df_nwalt_subwatershed_30m_rip_buffer, aes(x=log(area_sqm))) + geom_histogram(binwidth=1)
```


### Linear Regression

```{r}
df_nwalt_subwatershed_30m_rip_buffer %>% filter(site_id == 'A1' & wrriclass=='Urban')
```


```{r}
df_nwalt_subwatershed_30m_rip_buffer %>% filter(site_id == 'A110' & wrriclass=='Urban') %>% 
  group_by(year,site_id, wrriclass) %>%
  summarize(sum = sum(area_sqm)) %>%
  mutate(km=sum / 1e6) %>%
  ggplot(aes(x=year, y=km))+
  geom_line() +
  geom_point(aes(color=wrriclass))
  
df_nwalt_subwatershed_30m_rip_buffer %>%
  group_by(year,site_id, wrriclass) %>%
  summarize(sum = sum(area_sqm)) %>%
  mutate(km=sum / 1e6) %>%
  ggplot(aes(x=log(km))) + 
    geom_histogram()
```


```{r}
require("MASS")
lm.fit <- lm(formula=log(km)~year+wrriclass+site_id, data=df_nwalt_subwatershed_30m_rip_buffer %>% 
               # filter(site_id == 'A110' & wrriclass=='Agriculture') %>%
                group_by(year,site_id, wrriclass) %>%
                summarize(sum = sum(area_sqm)) %>%
                mutate(km=sum / 1e6) 
             )

summary(lm.fit)
```

confidence intervals 

```{r}
confint(lm.fit)
lm.fit$coefficients
```

Fill in missing values

```{r}
prediction_landclass <- unique(df_nwalt_subwatershed_30m_rip_buffer$wrriclass)
prediction_site_num <- unique(df_nwalt_subwatershed_30m_rip_buffer$site_id)
prediction_years <- seq(as.Date("01/01/1974", format="%m/%d/%Y"), as.Date("01/01/2021", format="%m/%d/%Y"), by="years")

#print(prediction_landclass)
#print(prediction_years)
prediction_values <- crossing(year=prediction_years,wrriclass=prediction_landclass, site_id=prediction_site_num)
confidence <- predict(lm.fit, prediction_values, interval = "confidence")
confidence
```

Prediction
```{r}
par(mfrow=c(2,2))
plot(lm.fit)
```
```{r}
predictions <- predict(lm.fit, data.frame(year=c(as.Date("01/01/2010",format="%m/%d/%Y" )), wrriclass=c('Urban'), site_id=c('A110')), interval = "prediction")
predictions
```


5. Create Variable Flood Plain Map


```{r, eval=FALSE}
rgrass7::execGRASS("r.mask", flags = c("r"))
rgrass7::execGRASS("r.mask", parameters = list(vector="subwatersheds"))
```
```{r, eval=FALSE}
rgrass7::execGRASS("g.region", flags = c("p"))

```

Generate the partial derivative dx and dy
```{r}
slope <- "slope"
aspect <- "aspect"
dx <- "dx"
dy <- "dy"
rgrass7::execGRASS("r.slope.aspect",
                   parameters=list(
                    elevation=dem,
                    dx=dx,
                    dy=dy
                  ),
                  flags = c('overwrite')
)

```

```{r calculateLanduse, eval=TRUE}




nwalt_years <- c("1974", "1982", "1992", "2002", "2012")
nwalt_prefix <- "nwalt_landuse_"

calucuteVariableFloodplain <- function(dem, date_range, landuse_file_prefix) {
  df_landuse_subwatershed <- NULL
  #Loop through each year of landuse data and calculate the total landuse area of each class per subwatershed per year. Return a single dataframe containing values for each year.
  for(year in date_range) {
    nwalt_data <- paste0(landuse_file_prefix, year, "@wrri10m")
    #output <- paste0(subwatershed_csv_prefix, year, ".csv")
    nwalt_date <- paste0("01/01/", year)
    depth <- paste0("nwalt_depth_",year)
    
    #Set manning values form landuse
    mancover <- paste0("mancover_nwalt_", year)
    rgrass7::execGRASS("r.recode",
                   parameters = list(
                     input=nwalt_data,
                     output=mancover,
                     rules="./nwalt_to_mannings.txt"
                   ))
    
    #Set variable rain cover values form landuse
    # raincover <- paste0("raincover_nwalt_", year)
    # rgrass7::execGRASS("r.recode",
    #                parameters = list(
    #                  input=nwalt_data,
    #                  output=raincover,
    #                  rules="./nwalt_to_raincover.txt"
    #                ))
    
    # Run simwe to simulate 100year flood event
    rgrass7::execGRASS("r.sim.water",
                   parameters = list(
                     elevation=dem,
                     dx=dx,
                     dy=dy,
                     #infil=,
                     #rain=raincover,
                     rain_value=50,
                     man=mancover,
                     depth="depth",
                     nwalkers=1000000,
                     niteraction=60,
                     output_step=10,
                     random_seed=5,
                     nprocs=14
                     ),
                     flags=c("overwrite", "s")
                   )
    
    
    # Extract areas withw water depth greater than 0.05m
    floodmap <- psate0("depth_filtered_", year)
    expression <- psate0(floodmap, " = if(",depth, " >= 0.05,1, null())")
    rgrass7::execGRASS("r.mapcalc", parameters = list(
      expression=expression
    ))
    
    # Crate floodplain by clumping together flooded areas
    floodplain <- paste0("floodplain_", year)
    rgrass7::execGRASS("r.neighbors",
                   parameters = list(
                     input=floodmap,
                     output=floodplain,
                     method="median",
                     size=9
                   ),
                   flags=c("overwrite", "c")
                   )
  }
}



```







Create vartiable Floodplain
r.mapcalc --overwrite expression=HR6_depth_filtered = if(HR6_depth.29@wrri >= 0.05, 1, null())

```{r}

rgrass7::execGRASS("r.mapcalc", parameters = list(
  expression="depth_filtered = if(depth.29 >= 0.05,1, null())"
))
```


r.neighbors -c --overwrite input=HR6_depth_filtered@wrri output=moving_stream_buffer method=median size=9

```{r}


rgrass7::execGRASS("r.neighbors",
                   parameters = list(
                     input="depth_filtered",
                     output="moving_stream_buffer",
                     method="median",
                     size=9
                   ),
                   flags=c("overwrite", "c")
                   )
```

## Results


